Numerous variables relating to 2016 election in 2021 US GSS^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-03-19 outputs/paper/paper.Rmd
ggplot

---
title: "Numerous variables relating to 2016 election in 2021 US GSS^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis.git]"
subtitle: "Possible factors effecting 2016 election"
author: 
  - SangWoong Lee
  - Young Suk
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence (what was done). Second sentence(what was found). Third sentence (why this matters). Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

```{r, echo=FALSE}
reduced_data %>%
  drop_na(age_group) %>%
  ggplot(aes(x = age_group, fill = age_group)) +
  geom_bar() +
  coord_flip() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Survey Respondents' Age",
       caption = "Figure 1: Distribution of survey respondents' age group") +
  theme(legend.position = "none")

@@

reduced_data %>%
  ggplot(aes(x = pres16, fill = pres16)) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Surveyee's vote choice of 2016 Presidential election",
       caption = "Figure 3: Distribution of survey respondents' vote choice") +
  theme(legend.position = "none")

# reduced_data %>%
#   ggplot(aes(x = age, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
#   geom_bar() +
#   scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
#   labs(fil = "Candidate")

reduced_data$pres16 <- factor(reduced_data$pres16, levels = c("Clinton","Trump","Other","Did not vote"))

@@

reduced_data %>%
  ggplot(aes(x = pres16, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

@@

reduced_data %>%
  ggplot(aes(x = gender, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

@@

reduced_data %>%
  ggplot(aes(x = born_US, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate")

reduced_data$Family_income <- factor(reduced_data$Family_income, 
                                     levels = c("Under $10,000","$10,000 ~ $19,999","$20,000 ~ $39,999","$40,000 ~ $59,999", 
                                                "$60,000 ~ $89,999","$90,000 ~ $129,999","$130,000 ~ $169,999","$170,000 or over"))
reduced_data %>%
  ggplot(aes(x = Family_income, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate") +
  coord_flip()

>>>>

---
title: "Numerous variables relating to 2016 election in 2021 US GSS^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]"
subtitle: "Possible factors effecting 2016 election"
author: 
  - SangWoong Lee
  - Young Suk
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence (what was done). Second sentence(what was found). Third sentence (why this matters). Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

```{r, echo=FALSE}
reduced_data$pres16 <- factor(reduced_data$pres16, levels = c("Clinton","Trump","Other","Did not vote"))

reduced_data$Family_income <- factor(reduced_data$Family_income, 
                                     levels = c("Under $10,000","$10,000 ~ $19,999","$20,000 ~ $39,999","$40,000 ~ $59,999", 
                                                "$60,000 ~ $89,999","$90,000 ~ $129,999","$130,000 ~ $169,999","$170,000 or over"))

reduced_data %>%
  drop_na(age_group) %>%
  ggplot(aes(x = age_group, fill = age_group)) +
  geom_bar() +
  coord_flip() +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Survey Respondents' Age",
       caption = "Figure 1: Distribution of survey respondents' age group") +
  theme(legend.position = "none")

@@

reduced_data %>%
  ggplot(aes(x = pres16, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Surveyee's Vote Choice of 2016 Presidential Election",
       caption = "Figure 3: Distribution of survey respondents' vote choice") +
  theme(legend.position = "none")

@@

reduced_data %>%
  ggplot(aes(x = born_US, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(x = element_blank(),
       y = element_blank(),
       title = "Surveyee's Vote Choice of 2016 Presidential Election by Brith Place",
       caption = "Figure 5: Distribution of survey respondents' vote choice by birth place",
       fil = "Candidate")

@@

# reduced_data %>%
#   ggplot(aes(x = gender, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
#   geom_bar() +
#   scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
#   labs(fil = "Candidate")

@@

reduced_data %>%
  ggplot(aes(x = Family_income, fill = factor(pres16, levels = c("Clinton", "Trump", "Other", "Did not vote")))) +
  geom_bar() +
  scale_fill_manual("Candidate", values = c("Clinton" = "#01378C", "Trump" = "#ff3d3d", "Other" = "#2cd18c", "Did not vote" = "#dede1b")) +
  labs(fil = "Candidate") +
  coord_flip()
